---
title: "Covid91 vaccine study Final2020"
author: "Jennifer Alvarez"
date: "October 22, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
OldData <-read.csv(file="covid91.csv" ,header=TRUE)
#recode aids to say covid and then remove the annoying "x" from the dataframe  
TrialData <- OldData %>% mutate(infected = recode(infected, aids ="covid", none = "OK" )) %>% select(-one_of("x")) 
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

$H_0$: The null hypothesis, is that among the target population,the vaccine has no effect on whether the contracts the virus or not. 

$H_A$: The alternative hypothesis, is that among the target population,the vaccine has an effect on whether the contracts the virus or not. 

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

```{r}
dataF=filter(TrialData, sex == "gal")
```



<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

##Graphical Discriptive Rresults



```{r}
DataF = filter(TrialData,sex=="gal")
barchartGC(~infected + treatment,data=DataF)
barchartGC(~infected + treatment,data=DataF, type="percent",main="Gals")

```

Among the females who contracted covid-19 twice as many took the placebo. Therefore, it appears that the vaccine does have a positive effect. 


```{r}
table1 <- xtabs(~infected + treatment,data=DataF)
rowPerc(table1)
colPerc(table1)
```

```{r}
fisher.test(table1)
```
The fisher  test shows the odds of getting Covid-19 are 0.4889403 to 1. the confidence interval for the odd ratio is 0.41 to 0.58.

##data for males   

```{r}
DataG = filter(TrialData,sex=="guy")
barchartGC(~infected + treatment,data=DataG)
barchartGC(~infected + treatment,data=DataG, type="percent",main="Guys")

```


It appears that the vaccine has a negative effect on the guys since they are more likely to get covid-19 if they receive the vaccine.
 
```{r}
table1 <- xtabs(~infected + treatment,data=DataG)
rowPerc(table1)
colPerc(table1)
```
 
 
```{r}
fisher.test(table1)
```
 

It appears that the vaccine has a negative effect on the guys since they are more likely to get covid-19 if they receive the vaccine.

## LBGTQ

```{r}
TrialData = filter(TrialData,LGBTQ=="gay")
barchartGC(~infected + treatment,data=TrialData)
barchartGC(~infected + treatment,data=TrialData, type="percent",main="gay")

```


It appears that the vaccine has a negative effect on the gays since they are more likely to get covid-19 if they receive the vaccine.
 
```{r}
table1 <- xtabs(~infected + treatment,data=TrialData)
rowPerc(table1)
colPerc(table1)
```
 
 
```{r}
fisher.test(table1)
```

## Drugusers

```{r}
TrialData = filter(TrialData,DrugUser=="yes")
barchartGC(~infected + treatment,data=TrialData)
barchartGC(~infected + treatment,data=TrialData, type="percent",main="DrugUser")

```


It appears that the vaccine has a positive effect on the Drug users since they are more likely to get covid-19 if they do not receive the vaccine.
 
```{r}
table1 <- xtabs(~infected + treatment,data=TrialData)
rowPerc(table1)
colPerc(table1)
```
 
 
```{r}
fisher.test(table1)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
According to the charts and numerical results, it seems that the females that took the drug are less likely to contract COVID-19. From the women who took the drug only 33.11 got infected with Covid-19. According to the inferential test that was 95.56% that were not infected making the vaccine very effective among the female population. Therefore, we fail to reject the Null hypothesis.  

According to the male and numerical results males who took the vaccine were contracting COVID-19. 58.16% of the males who took the treatment contracted coivd and only 48.54 were ok. From this data it seems that men are most likely to contract COVID-19 when given the vaccine. Therefore, we reject the Null hypothesis.   

According to the LGBTQ data 70.69% contracted Covid-19 when given the vaccine. 49.17% did not contract Covid-19 when given the vaccine. This shows that the vaccine had no postive effect in the LGBTQ population.   

According to the data from the drug users those who were given the vaccine had not contracted Covid-19. compared to those who were given the placebo had a 100% chance of contracting Covid -19. Therefore, we fail to reject the Null hypothosis among drug users.   




